---
title: "RT Group Differences"
author: "Haroon Popal"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set Up

```{r}
library(ggplot2)
library(readr)
library(stringr)
library(patchwork)
```

### Set paths
```{r}
knitr::opts_knit$set(root.dir = '/Users/hpopal/Google Drive/My Drive/dscn_lab/projects/social_reward/')

proj_dir <- '/Users/hpopal/Google Drive/My Drive/dscn_lab/projects/social_reward/'
data_dir <- paste(proj_dir ,'derivatives/task_socialreward/data/', sep='')
```

### Find participants
```{r, message=FALSE}
# Import participant ID data
subj_df <- read_tsv(paste(proj_dir,'participants.tsv', sep = ''))

# Fix participant IDs to match the directories in the data folder (e.g. sub-SCN101 -> SCN_101)

# Create function to get the subj numeric ID
get_subj_num <- function(subj_name){
  subj_num <- substr(subj_name, nchar(subj_name)-2, nchar(subj_name))
  paste('SCN_',subj_num, sep = '')
}

subj_df$participant_id <- lapply(subj_df$participant_id, get_subj_num)


print(paste('Found ',nrow(subj_df),' participants'))
```


# Data Cleaning
```{r}
rt_data <- data.frame(matrix(ncol=4, nrow=0))
colnames(rt_data) <- c('ParticipantID','Run',
                       'ConditionName','Correct_RT')

# Import data
for (subj in subj_df$participant_id) {
  # Find data for all runs
  run_files <- list.files(path=paste(data_dir,subj,'/', sep = ''), pattern="*\\-errors.csv", full.names=TRUE, recursive=TRUE)
  
  # Loop through runs and combine in to one df
  for (run_file in run_files) {
    temp_run_data <- read.csv(run_file)
    if (sum(temp_run_data$redcap_v_task) > 0) {
      next
    } else {
      temp_run_data_fltr <- temp_run_data[,which((names(temp_run_data) %in% names(rt_data))==TRUE)]
      rt_data <- rbind(rt_data, temp_run_data_fltr)
    }
  }
  
}

# Convert RTs to numeric type
rt_data$Correct_RT <- as.numeric(rt_data$Correct_RT)

```

```{r}
# Add group into to rt data
rt_data$group <- subj_df[match(rt_data$ParticipantID, subj_df$participant_id), 'group']
```

```{r}
# Create column for peer condition info
rt_data$Peer <- factor(sapply(list(rt_data$ConditionName),
                       str_split_i, pattern='_', i=2))
```

## Find number of missed trials
```{r}
sum(is.na(rt_data$Correct_RT))
```
Across all trials for all participants, there were 97 missed trials.



# Reaction Time Analyses

## Reaction time distribution
```{r}
ggplot(rt_data, aes(x=Correct_RT, fill=Peer)) + 
  geom_histogram(position='identity', alpha=0.5)
```

## Condition Means
```{r}
ggplot(data=rt_data, aes(x=Peer, y=Correct_RT)) +
  geom_bar(stat = 'summary', fun = 'mean') 
```

```{r}
model1 <- lm(Correct_RT ~ Peer, data=rt_data)

summary(model1)
```


```{r}
contr.treatment(3, base=3)
```

```{r}
# Create contrast
contrasts(rt_data$Peer) = contr.treatment(3, base=3)

model1 <- lm(Correct_RT ~ Peer, data=rt_data)

summary(model1)
```
Peer1 = Computer, Peer2 = DisPeer?


## Condition Means by Run

```{r}
ggplot(rt_data) + 
  geom_density(aes(x = Correct_RT, fill = Peer), alpha=0.5) + 
  facet_grid(rows = vars(Run))
```


### Contrast run 1 and 4 for each peer condition
```{r}
matrix(c(1,0,0,-1,0,0,0,0,0,0,0,0), ncol=3)
```

```{r}
contrasts_peer = contrasts(rt_data$Peer)
contrasts_peer[,1] = c(1,0,0)
contrasts_peer[,2] = c(0,1,0)

contrasts_run = contrasts(factor(rt_data$Run))
contrasts_run[,1] = c(1,0,0,-1)
contrasts_run[,2] = c(0,0,0,0)
contrasts_run[,3] = c(0,0,0,0)

model2 <- lm(Correct_RT ~ Peer*factor(Run), data=rt_data)

summary(model2)

```


# Group Differences

```{r}
p1 <- ggplot(rt_data[rt_data$group$group == 1,]) + 
      geom_density(aes(x = Correct_RT, fill = Peer), alpha=0.5) + 
      facet_grid(rows = vars(Run)) + 
      ggtitle('Not ASD') + 
      theme(plot.title = element_text(hjust = 0.5), legend.position="none") + 
      ylim(0, 2.5)
p2 <- ggplot(rt_data[rt_data$group$group == 2,]) + 
      geom_density(aes(x = Correct_RT, fill = Peer), alpha=0.5) + 
      facet_grid(rows = vars(Run)) + 
      ggtitle('ASD') + 
      theme(plot.title = element_text(hjust = 0.5), axis.title.y = element_blank()) + 
      ylim(0, 2.5)

p1 + p2
```

```{r}
model3 <- lm(Correct_RT ~ Peer + Run + group$group, data=rt_data)

summary(model3)
```

```{r}
ggplot(data=rt_data, aes(x=Peer, y=Correct_RT, fill=factor(Run), alpha=factor(group$group))) +
  geom_bar(stat = 'summary', fun = 'mean',
           position='dodge') + 
  scale_fill_discrete(name = "Run") + 
  scale_alpha_discrete(name = "Group", labels = c('Not ASD', 'ASD')) + 
  scale_alpha_manual(values=c(0.3,1))
```


# Next Steps?
Consider runs as longitudinal data and look at the rate of change of RT as a function of peer condition. Question: Do participants get faster reaction times over runs for similar peers compared to dissimilar peers?


